---
title: "Notes for cbspeeches Package"
author: "Joerg Reddig"
date: "16 Mai 2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


##--------Load Libraries------------##
library(readtext)
library(tidytext)
library(tidyverse)
library(readxl)

```


## Links for instructions

Tutorial: taking your data to go: <http://www.davekleinschmidt.com/r-packages/>

<http://rmhogervorst.nl/cleancode/blog/2016/03/07/create-package-for-dataset.html>
<http://kbroman.org/pkg_primer/pages/data.html>




## Create data folders

This command will create a data folder for the raw data

```{r, eval=FALSE}
# Create folder for raw data and copy it there:
devtools::use_data_raw()

```


## Load raw data into data frame

```{r, eval=TRUE, echo=FALSE, warning=FALSE}

# use readtext package to load the text data into a data frame
# https://cran.r-project.org/web/packages/readtext/vignettes/readtext_vignette.html
# https://uc-r.github.io/tidy_text



# read the speeches from the text/pdf files
cbspeeches <- readtext("data-raw/*",
                 docvarsfrom = "filenames", 
                 docvarnames = c("date", "institution", "speaker"),
                 dvsep = " - ")

# delete all special characters in the text
cbspeeches$text <- gsub('\n','', cbspeeches$text)
cbspeeches$text <- gsub('\"','', cbspeeches$text)

# cleaning up the date values, which might contain a letter for the speech
library(stringr)
cbspeeches$date <- str_replace(cbspeeches$date, "[ab]", "")


# change date column from string into  date format:
cbspeeches <- cbspeeches %>%
    mutate(date = as.Date(date, format = "%Y-%m-%d"))

```


## Enrich speeches data with metadata from excel file:

```{r}

speeches_overview <- read_excel("data/Raw Data - All Speeches 2006-2018.xlsx", sheet = "All speeches 2014-2018")
 
speeches_overview <- speeches_overview %>%
    select(c(Filename, City, Country, Event, Title, Language)) %>% 
    rename(doc_id = Filename, city = City, country = Country, event = Event, title = Title, language = Language)

cbspeeches <- inner_join(cbspeeches, speeches_overview)

rm(speeches_overview)

# test_set <- cbspeechesX %>% 
#   group_by(doc_id) %>% 
#   filter(n()>1)


```





Use the `use_data` function to save the data frame into the data folder of the package as an `rda` file:

```{r}
devtools::use_data(cbspeeches, overwrite = TRUE)

```


For better access from other analytical tools, make the data also available in csv file format: 

```{r}
write.csv(cbspeeches, file = "data/cbspeeches.csv", row.names = FALSE)
```



----------------------------------

## Create a help file

Create a file in the folder `R`:


```{r, eval=FALSE}
devtools::use_package_doc()
```


## Create documents

```{r, eval=FALSE}
devtools::document()
```



## Test and build

```{r, eval=FALSE}
devtools::check()
```




## Upload to Github

<https://github.com/joergreddig/cbspeeches.git>

Need to do this via the Git bash to connect the folder to a git repository. Then the push/pull functionality in RStudio works. 



----------------------------------

## Using the cbspeeches package


```{r, eval=FALSE}

devtools::install_github("joergreddig/cbspeeches")
data("cbspeeches")

```



In python, one can read the csv file: 

```{python, eval=FALSE}

import pandas as pd

url = "https://raw.githubusercontent.com/joergreddig/cbspeeches/master/data/cbspeeches.csv"

df = pd.read_csv(url, encoding = "latin1")

print(df.head(5))

```

